---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# visualizeR

<!-- badges: start -->
<!-- badges: end -->

The goal of visualizeR is to propose some utils to get REACH and AGORA colors, ready-to-go color palettes, and a few visualization functions (horizontal hist graph for instance).

## Installation

You can install the last version of visualizeR from
[GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("gnoblet/visualizeR", build_vignettes = TRUE)
```

## Roadmap

Roadmap is as follows:

- [ ] Add IMPACT's colors
- [ ] Add all color palettes from the internal documentation
- [ ] Add new types of visualization (e.g. dumbbell plot)
- [ ] Use examples
- [ ] Add some ease-map functions
- [ ] Add some interactive functions (maps and graphs)

## Request

Please, do not hesitate to pull request any new viz or colors or color palettes, or to email request any change (guillaume.noblet@reach-initiative.org or gnoblet@zaclys.net).


## Example

```{r example, eval = FALSE}
library(visualizeR)
# Get all saved REACH colors, named
cols_reach(unnamed = F)
```
